Overview

### 2024-11-10 notebooks/00_overview.qmd
update

---
title: Overview
description: Juno Orbits and Sunspot Numbers
jupyter: python3
---

```{python}
import matplotlib.pyplot as plt
from beforerr.matplotlib import unify_axes_fontsize, sync_legend_colors, set_linewidth, hide_legend_lines
```

@@

for dataset, name in zip(datasets, names):
    ds_variables = Variables(
        dataset=dataset,
        timerange=timerange,
    )
    df = ds_variables.to_pandas()
    df = df.rename(columns={c: f"{name}_{c}" for c in df.columns})
    dfs.append(df)
```

@@

```{python}
for p_config in config.panels:
    tvar2plot = process_panel(p_config)
    tvars2plot.append(tvar2plot)
```

@@

![](../figures/juno-hg-loc_sunspot-number.png)

>>>>

---
title: Overview
description: Juno Orbits and Sunspot Numbers
jupyter: python3
execute: 
  freeze: auto
---

```{python}
from IPython.display import clear_output
from juno import DEFAULT_TIMERANGE
import matplotlib.pyplot as plt
from beforerr.matplotlib import unify_axes_fontsize, sync_legend_colors, set_linewidth, hide_legend_lines
```

```{python}
timespan = (DEFAULT_TIMERANGE[1] - DEFAULT_TIMERANGE[0]).days
print(f"Time span: {timespan} days")
```

@@

for dataset, name in zip(datasets, names):
    ds_variables = Variables(
        dataset=dataset,
        timerange=timerange,
    )
    df = ds_variables.to_pandas()
    df = df.rename(columns={c: f"{name}_{c}" for c in df.columns})
    dfs.append(df)
clear_output()
```

@@

```{python}
for p_config in config.panels:
    tvar2plot = process_panel(p_config)
    tvars2plot.append(tvar2plot)

clear_output()
```

@@
